API design for machine learning software: experiences from the scikit-learn project

### 2013-09-09 paper.tex
twocolumn (examples need to be fixed)
correct the largest code snippets by putting them in figures

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{authblk}
%\usepackage{hyperref}
\usepackage{minted}
\usepackage[authoryear,round]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}

@@

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
The following snippet illustrates how to create a complex estimator
that computes both linear PCA and kernel PCA features on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selects the 10 best features in the combination according to an ANOVA test
and feeds those to an $\ell_2$-regularized logistic regression model.
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest

@@

Pipeline([("feat_union", union),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
         ]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}

@@

The snippet below illustrates how to find
hyper-parameter settings for an SVM classifier (SVC)
that maximize $F_1$ score
through 10-fold cross-validation on the training set.
\begin{pythoncode}
from sklearn.grid_search import GridSearchCV
from sklearn.svm import SVC

@@

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
In this example, two distinct hyper-parameter grids are
considered for the linear and radial basis function (RBF) kernels;
an SVM with a linear kernel accepts a $\gamma$ parameter, but ignores it,
so using a single parameter grid would waste computing time
trying out effectively equivalent settings.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, just like any other classifier:
it delegates the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).

>>>>

\documentclass[twocolumn]{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{dblfloatfix}
%\usepackage{hyperref}
\usepackage{minted}
\usepackage[authoryear,round]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}

@@

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
Figure~\ref{pca-union} illustrates how to create a complex estimator
that computes both linear PCA and kernel PCA features on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selects the 10 best features in the combination according to an ANOVA test
and feeds those to an $\ell_2$-regularized logistic regression model.

\begin{figure*}[b]
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest

@@

Pipeline([("feat_union", union),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
         ]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}
\caption{A union of linear PCA and kernel PCA for feature extraction.}
\label{pca-union}
\end{figure*}

@@

\begin{figure*}[b]
\begin{pythoncode}
from sklearn.grid_search import GridSearchCV
from sklearn.svm import SVC

@@

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
\caption{Optimizing the hyper-parameters of an SVM for $F_1$ score.}
\label{svm-gridsearch}
\end{figure*}

The code in Figure~\ref{svm-gridsearch} illustrates how to find
hyper-parameter settings for an SVM classifier (SVC)
that maximize $F_1$ score
through 10-fold cross-validation on the training set.
Two distinct hyper-parameter grids are
considered for the linear and radial basis function (RBF) kernels;
an SVM with a linear kernel accepts a $\gamma$ parameter, but ignores it,
so using a single parameter grid would waste computing time
trying out effectively equivalent settings.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, just like any other classifier:
it delegates the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).
